\bf Range Analysis for the IonMonkey JavaScript engine

### 2012-05-01 project-writings/paper.tex
Move some text to IonMonkey overview
Talk about the optimizations

\section{IonMonkey Overview}

\section{Implementation}
%% XXX: TODO
The IonMonkey compiler is somewhat loosely based on LLVM, in that it is an
imperative SSA compiler. IonMonkey takes the bytecode used by the SpiderMonkey
Javascript interpreter and compiles it to native code. Optimistic type
specialization is used, and if type assumptions fail, then execution ``bails
out'' to the interpreter.

IonMonkey has two intermediate languages. There is a ``Middle Intermediate
Representation'' which encompasses higher-level constructs such as lambdas,
objects, and strings. A variety of optimizations are performed, and then the
code is lowered to a ``Lower Intermediate Representation'' used for register
allocation and code generation.

@@

@@

>>>>

\section{IonMonkey Overview}
The IonMonkey compiler is somewhat loosely based on LLVM, in that it is an
imperative SSA compiler. IonMonkey takes the bytecode used by the SpiderMonkey
Javascript interpreter and compiles it to native code. Optimistic type
specialization is used, and if type assumptions fail, then execution ``bails
out'' to the interpreter.

IonMonkey has two intermediate languages. There is a ``Middle
Intermediate Representation'' (MIR) which encompasses higher-level
constructs such as lambdas, objects, and strings. A variety of
optimizations are performed, and then the code is lowered to a ``Lower
Intermediate Representation'' (LIR) used for register allocation and
code generation.

@@

\section{Implementation}

@@

\subsection{Overflow Check Elimination}
Overflow check elimination is implemented as part of the lowering pass
that generates the lower level intermediate representation (LIR) from
the middle intermediate representation (MIR). During lowering,
operations that can fail in such a way as to require a bailout have
``snapshots'' associated with them. During actual code generation,
instruction-specific checking code (overflow checking, in this case)
is emitted for operations that can fail and have snapshots associated
with them.

During lowering of arithmetic operations that can overflow, we check
whether the instructions range is finite; if it is, we supress
assigning a snapshot to the operation, eliminating the overflow check.

\subsection{Array Bounds Check Elimination}
We do not perform general array bounds check elimination. To do this
fully would require symbolic range analysis. Since IonMonkey already
does hoisting of bounds checks out of loops, we determined that the
effort would probably not be worth the gain.

We do eliminate bounds checks in one situation: when bounds checks
have been hoisted out of a loop, a check is added that specifically
bounds checks whether a value is greater than the array minimum index
(which, unfortunately, need not be zero). During lowering we will
eliminate this check if we can prove that the index is greater than
the minimum value.
